Paper

### 2021-12-15 Paper.Rmd
Wrote some paragraphs in the results section. I also added labels to the graphs that didn't have them. Let me know if you need me to write any more or change what I have.

---
title: "Paper"
author: "Nathan Hemenway"
date: "12/12/2021"
output: pdf_document
---

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red')

```
Write about difference between different crucial distances here.

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat3[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red')

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat4[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red')

#plot all vaccine curves
ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2]), color='red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2]), color='blue') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green')

>>>>

---
title: "Paper"
author: "Nathan Hemenway, Mark Hinds, Ian Hall"
date: "12/12/2021"
output: pdf_document
---

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

```
We started with 5 infected people in each simulation. In our first two simulations we were attempting to simulate a 6 and 26 foot infection distance. As you can see from the first two plots above, no one was infected from the 5 initial people who were infected. This is because in these examples we were trying to simulate a small town with a low population density. This is supposed to represent 1000 people in a town that is 36 million square feet or about 1.3 square miles. Since the population density is so low, it is extremely unlikely for two people to come in close enough contact to contract Covid-19 in our simulation. Our simulation does have its limitations and this may not be realistic. Our simulator is assuming every person is independent and randomly moves around from day to day. This doesn't account for hanging out with friends or going home to your family which are common situations where contracting Covid-19 is much more likely. Accounting for these factors might be possible, but its beyond the scope of this project. In our third simulation, we used a bootstrap confidence interval for an infection distance of about 60 feet. This distance was finally large enough that people still got infected despite the low population density. Based on the plot, the number of infected people will peak around 50 days and then slowly decrease as the majority of people start to recover and gain immunity. This simulation looks more realistic and follows the infection trend that viruses generally have.

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat1[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat2[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat3[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat3[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

@@

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat4[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat4[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

#plot all vaccine curves
ggplot() +
  geom_line(aes(x=1:51, y=plot_dat1[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat2[ ,2]), color='red') +
  geom_line(aes(x=1:51, y=plot_dat3[ ,2]), color='blue') +
  geom_line(aes(x=1:51, y=plot_dat4[ ,2]), color='green') + 
  labs(x="Day", y="People infected")

```
In the previous three simulations we assumed that no one was vaccinated, but we also wanted to look at how a vaccine would effect the spread of Covid-19. In these simulations we looked at 200 people with the same dimension parameters as before, but with only one person initially infected. We increased the infection distance since 200 people in a 1.3 square mile area is an even lower population density than before. All the parameters were held the same other than the vaccination rate for these simulations. The vaccine rates of the four examples were: 0, .5, .8, and .95. In the plot that shows the number of infected for each vaccination rate, black is 0 vaccinated, red is .5, blue is .8, and green is .95. As we would expect, when no one is vaccinated, the number of infected people peaks and falls much faster than when some people are vaccinated. It only took around 15 days to peak and nearly everyone was recovered by day 30. When no one was vaccinated it took much less time to get sick, but people also were recovered faster because everyone already had the virus. This is the idea of herd immunity that is often talked about, but it poses a massive problem with the hospitals. If everyone gets sick in a short period of time, hospitals can get overwhelmed and the death tolls can skyrocket due to lack of equipment and staff. Vaccinations aren't perfect, but they can help flatten the curve so the infection numbers don't peak as fast and also reduce the severity of the symptoms so less people need to be hospitalized. It is still possible to contract Covid-19 while vaccinated, but it is much less likely. As you can see in the last plot, as the vaccination rate increased, the longer it took for the cases to peak. The peak was also much lower than when no one was vaccinated and it took longer for the cases to completely disappear since people were being infected slower. This shows that a higher vaccination rate helps slow down the spread of Covid-19 even if it can't completely prevent it.
